Best Practices for Developing Monte Carlo Methodologies in Molecular Simulations [Article v\versionnumber]

### 2025-06-02 paper/paper.tex
Added muvt cb figure (and centering)

\begin{figure}
\includegraphics[width=6.5cm]{../figures/gibbs_particle.png}
\caption{
Gibbs ensemble transfer of the particle shown in blue from periodic domain $1$ to periodic domain $2$, and the reverse trial.
The total number of particles remains constant.
}
\label{fig:gibbs_particle}
\end{figure}

@@

\begin{figure}
\includegraphics[width=6.5cm]{../figures/gibbs_volume.png}
\caption{
Gibbs ensemble transfer of volume from periodic domain $1$ to periodic domain $2$, and the reverse trial.
The total volume remains constant and the particle positions are scaled as described in Section~\ref{sec:lhs_dv}.
}
\label{fig:gibbs_volume}
\end{figure}

@@

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/gibbs_particle.png}
\caption{
Gibbs ensemble transfer of the particle shown in blue from periodic domain $1$ to periodic domain $2$, and the reverse trial.
The total number of particles remains constant.
}
\label{fig:gibbs_particle}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/gibbs_volume.png}
\caption{
Gibbs ensemble transfer of volume from periodic domain $1$ to periodic domain $2$, and the reverse trial.
The total volume remains constant and the particle positions are scaled as described in Section~\ref{sec:lhs_dv}.
}
\label{fig:gibbs_volume}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=6.5cm]{../figures/muvt_cb.png}
\caption{
Multiple first bead configurational bias insertion and deletion considers randomly-generated positions for a newly inserted particle, shown by the dashed circles, in an existing fluid of particles, shown by the black circles.
The most favorable position has the highest Rosenbluth probability of selection, which is shown in blue due to excluded volume overlap of the other red positions with the existing fluid.
The deletion step does not consider other positions or particles for deletion, but to obey detailed balance, the Rosenbluth factor in the deletion step includes the existing position as well as other randomly-generated positions.
}
\label{fig:muvt_cb}
\end{centering}
\end{figure}
